\chapter{Trijunction of Majorana nanowires}

\section{Geometrical model in the strong coupling regime}

\begin{enumerate}
\item A single ballistic cavity can be used to couple multiple pairs of MBS selectively since - in a clean 2DEG - electron transport is completely determined by the cavity's shape and the leads' positions.
\item The minimum non-trivial number of MBS that can couple via a semiconducting cavity is three.
\item The coupling energy of each pair is extracted as the value of the lowest non-zero eigenvalue with respect to the cavity chemical potential.
\item Depending on the cavity's shape, certain levels carry the largest coupling for each pair of MBS.
\item For zero-mean Gaussian noise, there is a transition where the coupling vanishes for a standard deviation comparable to the chemical potential.
\end{enumerate}

\subsection{Phase dependence}
\begin{enumerate}
\item The phase relation is $4\pi$ periodic, but there is a phase shift controlled by the complex part of the hopping term.
\item It is anti-symmetric with respect to the central pairs, and it does not depend on the relative distance between the nanowires.
\end{enumerate}

\subsection{Size dependence}
\begin{enumerate}
\item The size of the system shows a transition from the low to the long junction regime of a Josephson junction with many levels inside the gap.
\item The coupling decays as the system gets bigger, but some geometries show an oscillatory pattern up to considerably large sizes.
\end{enumerate}


\section{Half-ring cavity}
\begin{enumerate}
\item Consider a narrow strip in a half ring shape with nanowires connected in a fork-like geometry.
\item Left and right MBS couple with the lowest levels as it would be a single level.
\item Magnitude of the coupling is similar for the central MBS pairs, but each cavity level couples independently.
\end{enumerate}

\section{Rectangular cavity}
\begin{enumerate}
\item Lowest sub band carries most of the coupling, while other bands' coupling is negligible.
\item While left and right MBS have large coupling, coupling to the central MBS depends on the side at which it is.
\item At certain distance between the nanowires, one pair dominates the coupling while the other two are canceled suggesting coupling mediated by semiclassical trajectories.
\end{enumerate}

\section{Triangular cavity}
\begin{enumerate}
\item At certain angle of the cavity, the coupling reaches a maximum for left and right MBS coupling.
\item The coupling of the central MBS pairs is controlled by the position of the central nanowire as previously.
\item Higher sub bands couple when the nanowires are attached to the diagonal sides of the triangle.
\end{enumerate}